The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2022-01-01 paper.tex
update

  The set of \Cref{governing-eq} is closed by using the Taub-Mathews equation of state (\citealt{Taub}; \citealt{TM_EOS})\
  that approximates the exact EoS \citep{Synge} for ultra-relativistically\
  hot gases coexisting with non-relativistically cold gases.

@@

  \begin{enumerate}
    \item X-ray:
       \begin{enumerate}
         \item Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
               using the MEKAL model (\citealt{Xray-1}; \citealt{Xray-2}; \citealt{Xray-3})\
               implemented in the utility XSPEC\citep{XSPEC}, assuming solar metallicity.
       \end{enumerate}
    \item Gamma-ray:
       \begin{enumerate}
         \item Leptonic process:\\
          The gamma-ray emission is produced by inverse Comptom scattering of the ISRF by CRe.
         \item Hadronic process:\\
          In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
          and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
          \begin{equation}
             \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
          \end{equation}
       \end{enumerate}
  \end{enumerate}

Note that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
which likely extends to a radius of $\sim$250 kpc (\citealt{halo-radius-1}; \citealt{halo-radius-2}),\
much bigger than our simulation box. Therefore, we first compute the X-ray emissivity\
from the simulated gas within a radius of 25 kpc away from the GC.
Then, beyond 25 kpc the gas is assumed to be isothermal with $T=10^6$ K and\
follows out to a radius of 250 kpc the observed density profile of \citep{temperature-MW}.

@@

Since the ISRF is dominated by the cosmic microwave background (CMB)\
at high latitudes and optical starlight at low latitudes,\

we integrate the incident photon energy from\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
$\epsilon_{\text{max}}=13.59$ eV (starlight).

@@

To evaluate the photon flux at the energy $\epsilon_{1}$ and\
take into account the perspective projection effect,
we integrate the emissivity along line-of-sights from the solar position:
\begin{equation}
I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl,
\end{equation}

>>>>

  The set of \Cref{governing-eq} is closed by using the Taub-Mathews equation of state \citep{Taub,TM_EOS}\
  that approximates the exact EoS \citep{Synge} for ultra-relativistically\
  hot gases coexisting with non-relativistically cold gases.

@@

  \begin{enumerate}
    \item X-ray:
       \begin{enumerate}
         \item Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
               using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
               implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.
       \end{enumerate}
    \item Gamma-ray:
       \begin{enumerate}
         \item Leptonic process:\\
          The gamma-ray emission is produced by inverse Comptom scattering of the ISRF by CRe.
         \item Hadronic process:\\
          In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
          and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
          \begin{equation}
             \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
          \end{equation}
       \end{enumerate}
  \end{enumerate}

Note that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
which likely extends to a radius of $\sim$250 kpc \citep{halo-radius-1,halo-radius-2},\
much bigger than our simulation box. Therefore, we first compute the X-ray emissivity\
from the simulated gas within a radius of 25 kpc away from the GC.
Then, beyond 25 kpc the gas is assumed to be isothermal with $T=10^6$ K and\
follows out to a radius of 250 kpc the observed density profile of \citep{temperature-MW}.

@@

We integrate the incident photon energy from\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
$\epsilon_{\text{max}}=13.59$ eV (starlight) in order to\
facilitate a reliable interpretation.

@@

To evaluate the simulated photon flux $I$ at the energy $\epsilon_{1}$ and\
take into account the perspective projection effect,
we integrate the emissivity over line-of-sights from the solar position:
\begin{equation}
I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl.
\end{equation}
